%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.3 (29/10/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{multicol}


\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Shannon} % Your first name
\familyname{Gallagher} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\address{FMS 325; Carnegie Mellon University}{5000 Forbes Ave.; Pittsburgh, PA 15219}
\mobile{(724) 504-8990}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{sgallagh@stat.cmu.edu}
\homepage{stat.cmu.edu/~sgallagh/}{stat.cmu.edu/$\sim$sgallagh/} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[70pt][0.4pt]{pictures/shannon} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}

% %----------------------------------------------------------------------------------------
% %	COVER LETTER
% %----------------------------------------------------------------------------------------

% % To remove the cover letter, comment out this entire block

% \clearpage

% \recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
% \date{\today} % Letter date
% \opening{Dear Sir or Madam,} % Opening greeting
% \closing{Sincerely yours,} % Closing phrase
% \enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

% \makelettertitle % Print letter title

% \lipsum[1-2] % Dummy text
% \lipsum[4] % Dummy text

% \makeletterclosing % Print letter signature

% \newpage

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title
\vspace{-3em}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2014--2019}{PhD in Statistics \& Data Science}{Carnegie Mellon University}{}{}{}  % Arguments not required can be left empty
\cventry{2014-2015}{MS in Statistics}{Carnegie Mellon University}{}{}{}  % Arguments not required can be left empty
\cventry{2010--2014}{BS in Mathematical Sciences}{Carnegie Mellon University}{}{}{University and College Honors}  % Arguments not required can be left empty

\section{Dissertation}
\cvitem{Expected 2019}{"Catalyst: agents of change.  A statistical analysis of compartment and agent-based models."  Advisor: William F. Eddy.  Committee:  Joel Greenhouse, Howard Seltman,  and Samuel L. Ventura.}

\section{Publications and Reports}
\cvitem{2018}{\href{https://www.tandfonline.com/doi/abs/10.1080/10618600.2018.1442342}{Gallagher, S., Richardson, L., Ventura, S.L., and Eddy, W.F. ``SPEW: Synthetic Populations  and Ecosystems of the World.''  \textit{Journal of Computational and Graphical Statistics}, 2018.}}
\cvitem{2018}{Gallagher, S. and Eddy, W.F. ``On the stochastic equivalence of compartment and agent-based models.'' In preparation, 2018.}
\cvitem{2018}{Gallagher, S., Chang, A., and Eddy, W.F. ``An analysis of nine ways to estimate $R_0$ in the SIR model.'' In preparation, 2018.}
\cvitem{2018}{Gallagher, S., Frisoli, K., and Luby, A. ``Opening up the (surface) of the court in tennis grand slams'' In preparation, 2018.}


\section{Selected Presentations and Posters}
\cvitem{2018}{\href{http://stat.cmu.edu/~sgallagh/papers/courtsports-cmsac2018.pdf}{``Opening up the (court) surface in tennis grand slams.''}  \textbf{Honorable Mention} Presentation.  Joint work with Kayla Frisoli and Amanda Luby.  Carnegie Mellon Sports Analytics Conference.  Pittsburgh, PA.}
\cvitem{2018}{\href{http://stat.cmu.edu/~sgallagh/papers/jsm2018-gallagher.pdf}{``Catalyst: agents of change.''  Poster. Advisor: William F. Eddy.  Committee:  Joel Greenhouse, Howard Seltman,  and Samuel L. Ventura.  Joint Statistical Meetings.  Vancouver, BC.}}
\cvitem{2017}{\href{http://www.stat.cmu.edu/~sgallagh/papers/jsm-2017-slides.pdf}{``Comparing Compartment and Agent-based Models.''} Presentation. Advisor: William F. Eddy.  Committee:  Joel Greenhouse, Howard Seltman,  and Samuel L. Ventura.  Joint Statistical Meetings.  Baltimore, MD.}
\cvitem{2017}{``Generating Synthetic Ecosystems: A Tutorial''. \textbf{Invited presentation.}   Joint work with Lee Richardson, Samuel Ventura, and William Eddy.  International Conference on Synthetic Populations.  Lucca, Italy. }
\cvitem{2016}{ \href{http://www.stat.cmu.edu/~sgallagh/papers/WSDS\_panel.pdf}{``Women in Statistics at Carnegie Mellon University.''}  Joint work with Purvasha Chakravarti. Presentation.   Women in Statistics and Data Science.  Charlotte, NC.}
\cvitem{2016}{  \href{http://www.stat.cmu.edu/~sgallagh/papers/poster\_wsds.pdf}{``Statistical Modelling of Infectious Diseases: Influenza and the `Next Disease.{'}''} Poster.  Joint work with Roni Rosenfeld, Ryan Tibshirani, Lee Richardson, Samuel Ventura, and William Eddy. Women in Statistics and Data Science.  Charlotte, NC.}
\cvitem{2016}{\href{http://www.stat.cmu.edu/~sgallagh/papers/midas\_meeting\_2016\_gallagher.pdf}{``Services for the MIDAS Network: Visualization and Synthetic Ecosystems.''}  Poster.  Joint work with Lee Richardson, Samuel Ventura, and William Eddy.  MIDAS National Conference.  Washington D.C.}
\cvitem{2016}{    \href{http://www.stat.cmu.edu/~sgallagh/papers/gallagher_buffalo.pdf}{``From Forecasting the Flu to Predicting the `Next' Disease.''} Poster. Joint work with Roni Rosenfeld, Ryan Tibshirani, Lee Richardson, Samuel Ventura, and William Eddy. UP-STAT.  Buffalo, NY. }


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Honors and Awards}
\cvitem{2018}{\href{https://cmusportsanalytics.com/conference2018.html}{Carnegie Mellon University Sports Analytics Conference Reproducible Paper Competition \textbf{Honorable Mention} and \textbf{\$1,000 award}}.}
\cvitem{2014, 2018}{ \href{https://www.amstat.org/ASA/Your-Career/Awards/Gertrude-M-Cox-Scholarship.aspx}{Gertrude M. Cox Scholarship \textbf{Honorable Mention};  ASA Committee on Women in Statistics and the Caucus for Women in Statistics.} }
\cvitem{2018}{Scholarship recipient for \href{http://www.biostat.washington.edu/suminst/sismid}{the Summer Institute in Statistics and Modeling} (tuition and travel stipend). University of Washington, Seattle, WA.}
\cvitem{2017}{\href{stats.research.att.com/grad-symposium}{AT\&T Labs Graduate Student Symposium Selected Presenter}. One of fourteen PhD students out of 79 applicants selected to give a presentation on ongoing research to AT\&T researchers in NYC.  \textbf{Awarded \$800} in travel funding.}
\cvitem{2016}{  \href{https://midas-publichealth-hack-3336.devpost.com/}{MIDAS MISSION Public Health \textbf{Hackathon Champion} with \textbf{\$3,000} prize. }}
\cvitem{2016}{  \href{http://www.up-stat.org/conference/Index/}{UP-STAT \textbf{2nd Place Student} Presentation}. }
\cvitem{2014}{\href{https://www.cmu.edu/mcs/news/pressreleases/2014/0514-gallagher-resnik.html}{Judith A. Resnik Award for Outstanding Women in the Sciences; Carnegie Mellon University.} }
\cvitem{2013}{  \href{http://archive.constantcontact.com/fs157/1102665924422/archive/1114499299154.html}{Phi Beta Kappa Honor Society.}  }

\section{Software}
\cvitem{2018-Present}{\texttt{catalyst}: Compartment and Agent-based model Temporal Analysis and Testing.  In development.}
\cvitem{2016-Present}{ \href{http://www.stat.cmu.edu/~/spew}{\texttt{spew}}: \texttt{R} package for synthetic ecosystem generation.  Lee Richardson, Shannon Gallagher, Samuel L. Ventura, and William F. Eddy.  Available on \href{https://cran.r-project.org/web/packages/spew/index.html}{\texttt{CRAN}}.}
\cvitem{2017}{\href{http://shiny.stat.cmu.edu:3838/sgallagh/spew_dl/}{\texttt{spew\_dl}}: \texttt{R} Shiny application to easily browse our synthetic ecosystems produced by \texttt{spew}. Shannon Gallagher, Lee Richardson, Samuel L. Ventura, and William F. Eddy.}
\cvitem{2016}{ \href{http://shiny.stat.cmu.edu:3838/sgallagh/spewview}{\texttt{spewview}}: \texttt{R} Shiny application for infectious disease visualization. Shannon Gallagher and Lee Richardson.}



\section{Research, Teaching, and Work Experience}

\cvitem{2014-Present}{\textbf{Research Assistant,} Carnegie Mellon University.  Generated high-resolution synthetic ecosystem of U.S. and 70+ countries for use in agent-based models for transmission of disease.}
\cvitem{2012-Present}{\textbf{Teaching Assistant}, Carnegie Mellon University.  Oversaw lab for 100 students, organized, and led review sessions for a variety of statistics and mathematics classes including Epidemiology, Statistical Computing, Intro to Probability, Advanced Undergraduate Research, Concepts of Mathematics, and Calc 3D.}

\cvitem{2015}{\textbf{Graduate Intern}, PNC.  Scraped and analyzed social media data for sentiment analysis. Parallelized code with Hadoop.}

 % \cvitem{2012}{\textbf{Director's Summer Program Participant}. National Security Agency. Implemented and optimized a combinatorial algorithm in \texttt{C++}.  Briefed Director of NSA on research findings.  Fort Meade, MD.}



\section{Programming Languages}
\cvitem{}{\texttt{R} (expert),  \texttt{julia} (proficient),  \texttt{html} (intermediate) \texttt{Python} (intermediate), \texttt{C++} (intermediate), \texttt{C} (intermediate), \texttt{SQL} (some experience), \texttt{jekyll} (some experience)}



\section{Professional Service
}
\cvitem{2018-Present}{\textbf{PI}.  \href{https://www.cmu.edu/proseed/proseed-seed-grants/crosswalk.html}{ProSEED/Crosswalk recipient} for \$1600 to seed a mentorship program across all levels of students within the Stat\&DS community.}
\cvitem{2017-Present}{\textbf{Co-President}. \href{http://cmuwomeninstats.blogspot.com/}{Carnegie Mellon University Women in Statistics.
    \begin{itemize}
    \item Organized Women in \href{http://stat.cmu.edu/wids}{Data Science Pittsburgh @CMU} as an Executive Committee Member.  Invited speakers and sponsors, helped organize venue logistics, sent out invitations for attendance, and created the \href{http://stat.cmu.edu/wids}{website} (2018).
    \item Maintained \href{http://stat.cmu.edu/womeninstats}{Women in Statistics website} (2017-Present).
    \item  Organized a seminar by a former PhD student about her experiences as a post-doc at Harvard Biostatistics (2017).
    \item Organized a panel about applying to graduate school for 30+ undergraduate and masters students (2017).
    \item Organized dinner with new dean of Mellon College of Science (2017).
    \end{itemize} \hspace{1em}\vspace{-1em}}} 
\cvitem{2016-Present}{\textbf{Reviewer}. Statistics in Medicine and Journal of Quantitative Analysis in Sports.}
\cvitem{2016-2018}{ \textbf{Co-Organizer}. \href{https://www.meetup.com/Pittsburgh-useR-Group/}{Pittsburgh use\texttt{R}}.  Organized meet-ups for 30+ members on a variety of topics including cross-language coding and integrating \texttt{R} with \texttt{github}.}
\cvitem{2016-2017}{\textbf{Judge and volunteer}. \href{http://www.stat.cmu.edu/tartandatasciencecup/}{Tartan Data Science Cup -- 3 to date.}}
\cvitem{2016-2017}{\textbf{Vice President}. \href{http://cmuwomeninstats.blogspot.com/}{Carnegie Mellon University Women in Statistics}}
\cvitem{2016}{\textbf{Presenter}.  \href{http://www.stat.cmu.edu/~sgallagh/coding_for_girls/mydeck/index.html\#1}{Coding for Girls.}}


\section{Relevant Course Work}

  \begin{multicols}{2}
\begin{itemize}
\item Machine Learning I \& II (\textbf{Grad})
\item 	Statistical Computing (\textbf{Grad})
\item 	Modern Regression (\textbf{Grad})
\item Hierarchical Models (\textbf{Grad})
\item 	Multivariate Methods \& Data Mining
\item 	Data Matching and Record Linkage
\item 	Advanced Methods for Data Analysis


\item 	Epidemiology


\end{itemize}


\end{multicols}

\section{Volunteering}
\cvitem{2016-Present}{ \textbf{Family House}.  Make meals for families with members in the hospital approximately every other month.}
\cvitem{2017-2018}{\textbf{Stat Help Network}. Hold anonymous ``office hours'' for graduate students within the Statistics and Data Science Department in order to support students.}



\end{document}